Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns

### 2019-08-28 ms/manuscript.Rmd
Use format_pval

```{r corr-numbers}
stipe_pval <- pic_results %>% filter(trait == "stipe") %>% pull(p.value) %>% signif(2)
width_pval <- pic_results %>% filter(trait == "width") %>% pull(p.value) %>% signif(2)
dissection_pval <- pic_results %>% filter(trait == "dissection") %>% pull(p.value) %>% signif(2)
morphotype_pval <- correlated_evo_test %>% filter(trait == "morphotype") %>% pull(pval) %>% signif(2)
```

Most sporophyte traits, including all those related to plant size, are significantly correlated with growth habit while taking phylogeny into account (\tab \@ref(tab:pics)). Epiphytic species tend to have smaller values for all traits (\tab \@ref(tab:pics); contrasts were made by subtracting epiphytic from terrestrial values). Short stipe length in particular appears to be strongly correlated with epiphytic growth (phylogenetically independent contrasts, \pval = `r stipe_pval`), as well as frond width (\pval = `r width_pval`) and degree of laminae dissection (\pval = `r dissection_pval`). For the gametophyte traits, only morphotype (non-cordate vs. cordate) was significantly correlated with growth habit (Pagel's test of correlated evolution, \pval = `r morphotype_pval`; \tab \@ref(tab:corr-evo)). Similar results were obtained using the "strict" dataset (\tab S5).

>>>>

```{r corr-numbers}
stipe_pval <- pic_results %>% filter(trait == "stipe") %>% pull(p.value) %>% format_pval(., equals_sign = TRUE)
width_pval <- pic_results %>% filter(trait == "width") %>% pull(p.value) %>% format_pval(., equals_sign = TRUE)
dissection_pval <- pic_results %>% filter(trait == "dissection") %>% pull(p.value) %>% format_pval(., equals_sign = TRUE)
morphotype_pval <- correlated_evo_test %>% filter(trait == "morphotype") %>% pull(pval) %>% format_pval(., equals_sign = TRUE)
```

Most sporophyte traits, including all those related to plant size, are significantly correlated with growth habit while taking phylogeny into account (\tab \@ref(tab:pics)). Epiphytic species tend to have smaller values for all traits (\tab \@ref(tab:pics); contrasts were made by subtracting epiphytic from terrestrial values). Short stipe length in particular appears to be strongly correlated with epiphytic growth (phylogenetically independent contrasts, \pval `r stipe_pval`), as well as frond width (\pval `r width_pval`) and degree of laminae dissection (\pval `r dissection_pval`). For the gametophyte traits, only morphotype (non-cordate vs. cordate) was significantly correlated with growth habit (Pagel's test of correlated evolution, \pval `r morphotype_pval`; \tab \@ref(tab:corr-evo)). Similar results were obtained using the "strict" dataset (\tab S5).
